A highly-available move operation for replicated trees and distributed filesystems

### 2020-06-08 paper/move-op.tex
Add photos and biographies

\bibliographystyle{IEEEtran}
\bibliography{references}{}
\end{document}

>>>>

\bibliographystyle{IEEEtran}
\bibliography{references}{}
\newpage

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photo-martin.jpg}}]{Martin Kleppmann}
is a Senior Research Associate at the University of Cambridge. His research spans distributed systems, databases, security, and formal verification, with a particular focus on decentralised collaboration software and CRDTs. His book \emph{Designing Data-Intensive Applications} was published in 2017 and has been translated into six languages. Previously, he worked as a software engineer and entrepreneur at several internet companies, including Rapportive and LinkedIn.
\end{IEEEbiography}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photo-dominic.jpg}}]{Dominic P.\ Mulligan}
is a Staff Research Engineer in the Security Group at Arm Research, UK.  Prior to moving to Arm, he worked as a postdoctoral researcher at the Universities of Cambridge and Bologna, Italy, investigating the formal specification and verification of systems software such as C compilers and linkers.  His interests include formal verification, distributed systems, and privacy and security.
\end{IEEEbiography}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photo-victor.jpg}}]{Victor B.\ F.\ Gomes}
received a diplôme d'ingénieur from INSA Lyon and a PhD degree from the University of Sheffield. He was a research associate at the University of Cambridge from 2016 to 2019 and he is currently working at Google. His main research interests are semantics of programming languages, formal verification via theorem prover assistants and algebraic approaches for program verification.
\end{IEEEbiography}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photo-alastair.jpg}}]{Alastair R.\ Beresford}
is Professor of Computer Security in the Department of Computer Science at the University of Cambridge. His research work explores the security and privacy of large-scale distributed systems, with a particular focus on networked mobile devices such as smartphones, tablets and laptops. He looks at the security and privacy of the devices themselves, as well as the security and privacy problems induced by the interaction between mobile devices and cloud-based Internet services.
\end{IEEEbiography}
\vfill
\end{document}
